\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-09-27 paper.tex
add more to intro

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
Site~\autocite{unesco} and one of the most popular tourist destinations in
Japan~\autocite{japanguide2019}. However, much of the historic information at
the site is lost on visitors because it is not readily available to non-Japanese
speakers.

@@

\subsubsection{GPS Functionality}
\label{sec:gpsFunctionality}
The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke
changes in the app, such as playing audio and displaying different images.
Originally, we planned to mark regions by singular points, and trigger that
region if the user was within a certain radius of that point.
Implementation-wise, this would have been much simpler, but obviously limits
possible tour designs. Consequently, we decided at an early stage to
accommodate regions with arbitrary shape and size.  In the implementation, we
provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
we eventually dropped support for regions triggered by distance.

>>>>

\usepackage{lipsum} % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex} % citations
\usepackage[page, titletoc, title]{appendix} % labeled appendices
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref} % hyperlinks
\usepackage{setspace} % setting custom spacing
\usepackage{tabulary} % nicer tables
\usepackage{CJKutf8} % for Japanese UTF-8 characters

@@

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}. AR technology can provide accessible
information to tourists and art viewers that they would not be able to get any
other way. Kinkaku-ji, the ``golden pavilion'' of Kyoto, is the perfect example
of this~\autocite{bornoff2000}. Kinkaku-ji is a UNESCO World Heritage
Site~\autocite{unesco} and one of the most popular tourist destinations in
Japan~\autocite{japanguide2019}. The Golden Pavilion is a magnificent sight to
behold, but the gardens and grounds are the true beauty of Kinkaku-ji. It is a
living masterpiece of Zen Buddhist landscape design, expanding on the natural
beauty of Kyoto's forests and mountains through the practice of borrowed
scenery~\autocite{kuitert2002}.

However, much of the historic information at the site is lost on visitors
because it is not readily available to non-Japanese speakers. What few signs and
displays exist are presented only in Japanese, and do not provide most of the
history and context necessary to fully understand Kinkaku-ji.

@@

ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{goth}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour.

\subsubsection{GPS Functionality}
\label{sec:gpsFunctionality}

The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke
changes in the app, such as playing audio and displaying different images.
Originally, we planned to mark regions by singular points, and trigger that
region if the user was within a certain radius of that point.
Implementation-wise, this would have been much simpler, but obviously limits
possible tour designs. Consequently, we decided at an early stage to
accommodate regions with arbitrary shape and size.  In the implementation, we
provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
we eventually dropped support for regions triggered by distance.
